---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# ggrough2

**ggrough2** converts ggplot2 visualizations into hand-drawn, sketch-style graphics. It works by rendering your plot to SVG and then re-drawing every element using [Rough.js](https://roughjs.com/).

The output is an [htmlwidget](https://www.htmlwidgets.org/).

## Installation

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("schochastics/ggrough2")
```

## Basic usage

Pass any ggplot object to `rough_plot()`.

```{r basic, eval = TRUE,out.width = 800}
library(ggplot2)
library(ggrough2)

p <- ggplot(mpg, aes(displ, hwy)) +
  geom_point()

rough_plot(p, width = 7, height = 5)
```

## Fill styles

The `fill_style` argument controls how filled shapes (bars, areas, boxes) are
drawn. Available options are `"hachure"` (default), `"cross-hatch"`, `"dots"`,
`"zigzag"`, `"dashed"`, `"zigzag-line"`, and `"solid"`.

```{r fill-styles, eval = FALSE}
p <- ggplot(diamonds, aes(cut)) +
  geom_bar()

rough_plot(p, fill_style = "cross-hatch")
rough_plot(p, fill_style = "dots")
```

## Background fill style

Use `bg_fill_style` to control the fill style of panel and plot backgrounds
independently from data elements. By default backgrounds are `"solid"` while
geoms use `"hachure"`.

```{r bg-fill, eval = FALSE}
p <- ggplot(mpg, aes(displ, hwy)) +
  geom_point(size = 3) +
  theme(
    panel.background = element_rect(fill = "lightyellow"),
    plot.background  = element_rect(fill = "lightyellow")
  )

# solid panel background, hachure geoms (default)
rough_plot(p)

# dotted panel background, cross-hatch geoms
rough_plot(p, fill_style = "cross-hatch", bg_fill_style = "dots")
```

## Roughness and bowing

`roughness` controls how jagged the lines are (0 = perfectly smooth, up to 10).
`bowing` controls how much straight lines bow outwards. Higher values create a more exaggerated hand-drawn effect.

```{r roughness, eval = FALSE}
p <- ggplot(mpg, aes(class)) +
  geom_bar()

rough_plot(p, roughness = 3, bowing = 2)
```

## Reproducible output

Rough.js uses randomness to vary each stroke. Pass `seed` to get a stable result.

```{r seed, eval = FALSE}
rough_plot(p, seed = 42)
```

## Custom fonts

Text labels default to the bundled [Indie Flower](https://fonts.google.com/specimen/Indie+Flower) handwritten font. Supply any `.ttf`, `.otf`, `.woff`, or `.woff2` file to use a different one, or set `font = NULL` to keep the original plot fonts.

```{r font, eval = FALSE}
# custom font
rough_plot(p, font = "path/to/myfont.ttf")

# keep the plot's original fonts
rough_plot(p, font = NULL)
```

## Saving output

Export to a standalone HTML file (no external dependencies):

```{r save-html, eval = FALSE}
save_rough_html(p, "my_plot.html")
```

Export to PNG or SVG (requires the [webshot2](https://rstudio.github.io/webshot2/) package and a Chrome/Chromium installation):

```{r save-image, eval = FALSE}
save_rough_image(p, "my_plot.png")
save_rough_image(p, "my_plot.svg")
```
